---
title: "Basic use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic-use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(navr)
obj <- navr_object
```

## Getters

### Filtering time
Navr object can be filtered by time with `filter_times` function. The function takes either real time as is in the `$timestamp` column or can take `time_since_start` times if `zero_based = TRUE`. For that your object needs to be preprocessed with either `add_time_since_start`, `add_time_columns` or `add_columns_navr`. See loading and preprocessing vignette.

So if you say for example only the first 10 seconds of your obj, you can do the following

```{r}
obj_prep <- prepare_navr(obj)
obj_first10 <- filter_times(obj_prep, c(0,10), zero_based=TRUE)
```

If you on the other hand want to filter as per real timestamps, you can simply do so with

```{r}
head(obj_prep$data[,1:5])
obj_filtered <- filter_times(obj_prep, c(58250,58255))
head(obj_filtered$data[,1:5])
```
